True versus apparent shapes of bow shocks and bow waves

### 2017-11-11 papers/Paper1/sec-thin-shell.tex
Improve ancantoid figures

\section{Thin-shell hydrodynamic bow shock models}
\label{sec:crw-scenario}

@@

For the wind--wind case, a family of solutions are found that depend on
the value of \(\beta\), the wind momentum ratio, see
Figure~\ref{fig:crw-schema}, equations~(\ref{eq:stagnation-radius},
\ref{eq:beta-definition}), and surrounding discussion in
\S~\ref{sec:intro}.  We propose that these shapes be called
\textit{cantoids}.  The exact solution for the cantoid shapes
(eqs.~[23, 24] of \CRW{}) is only obtainable in implicit form, but an
approximate explicit solution (eq.~[26] of \CRW{}) is very accurate
for \(\beta \le 0.1\).  The wilkinoid shape corresponds to the
\(\beta \to 0\) limit of the cantoids.  Note that \CRW{}'s \(z\) and
\(r\) axes, which we use in our Figure~\ref{fig:crw-schema},
correspond respectively to the \(x\) and \(y\) axes in
sections~\ref{sec:projection} and \ref{sec:conic} of the current
paper.  By always placing the weaker of the two winds at the origin,
it is only necessary to consider \(\beta \le 1\).

@@

A generalization of the cantoids to the case of an
anisotropic\footnote{Note that the wind anisotropy axis must be
  aligned with the star--star axis to maintain cylindrical symmetry.}
inner wind is developed in Appendix~\ref{app:ancantoid}, giving rise
to what we call \textit{ancantoids}, which depend on an anisotropy
index, \(k\), in addition to \(\beta\).  The resulting shapes are shown in
Figure~\ref{fig:r-beta} for three different values of \(\beta\).  There is
a general tendency for the bows to be flatter and more open with
increasing \(\beta\), while at a given \(\beta\) it is the cantoid (black
lines) that is most open

\subsection{Characteristic Radii}
$R_0$ is obtained directly from equation (27) of \CRW{} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.
%Here goes a little introduction
For the rest of the radii we need a relation between $\theta$ and $\theta_1$ as follows:

\begin{align}
\theta_1\cot\theta_1 -1 = 2\beta I_k(\theta) \cot\theta - \frac{2\beta}{k+2}\left(1-\cos^{k+2}\theta\right)
\label{eq:th1th}
\end{align}

Equation (\ref{eq:th1th}) is reduced to equation (24) of \CRW{} when $k=0$.
We can obtain $R_{90}$ by following the process shown in appendix \ref{app:r90-analytic},
which lead us to a solution for $B \equiv \frac{R_{90}}{R_0}$:

\begin{align}
\tilde{R}_{90} = \frac{\sqrt(3\xi)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
\label{eq:B}
\end{align}

Now, the solution for $R_c$ is explained in appendix \ref{app:rc-analytic},
which lead us to derive the radius of curvature at the symmetry axis:

\begin{align}
R_c &= R_0\left(1-2\gamma\right)^{-1} \label{eq:Rcurv} \\
\mathrm{where:~} & \gamma = \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}(1-2\beta^{1/2})
\end{align}

Finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of
conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (\ref{eq:Thc})

\begin{align}
\tan^2\theta_c &= \left| \frac{3\xi\left(1+\beta^{1/2}\right)^2}{\left(1-\xi\beta\right)^2\left(1+\frac{1}{5}\xi\beta\right)}-\frac{2}{\left(1-2\gamma\right)}\right| 
\label{eq:thc-CRW}
\end{align}

\begin{figure}
\begin{tabular}{c}
\includegraphics[width=\linewidth]{figs/AB-beta-log} \\
\includegraphics[width=\linewidth]{figs/thc-beta-log}
\end{tabular}
\caption{Top: Characteristic radii, $\tilde{R}_c = R_c/R_0$ (solid lines) and $\tilde{R}_{90}
  = R_{90}/R_0$ (dashed lines)
  vs $\beta$, calculated from quadric fits to the generalized CRW
  solutions with varying degrees of isotropy $\xi$.  Bottom: Conic
  angle $\theta_c$ vs $\beta$ for the bow 
  shock head (solid lines) and the bow shock tail (dashed lines).}
\label{fig:rad-beta}
\end{figure}

% Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii,
%being $R_0$ the
%easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).

With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
momenta and different density distributions. Figure \ref{fig:rad-beta} shows equations ( \ref{eq:B}), (\ref{eq:Rcurv}) and (\ref{eq:thc-CRW}) for different anisotropy indexes.

\subsection{Special Case: Isotropic Wind/Parallel Flow Interaction Problem}

This problem has already been solved in \citet{Wilkin:1996a} and \CRW{}, which have an explicit form for the shell shape, given by:

\begin{align}
  R(\theta) = R_0\csc\theta\left[3(1-\theta\cot\theta)\right]^{1/2} \label{eq:R-Wilkin}
\end{align}
Where:
\begin{align}
  R_0 = \left(\frac{\dot{M}_wv_w}{4\pi\rho_a v_a^2}\right)^{1/2}
\end{align}
And $\rho_a$ and $v_a$ being the density and the velocity of the Parallel wind, respectively.
The characteristic radii are given by:
\begin{align}
  \tilde{R}_{90} &= \sqrt{3} \\
  \tilde{R}_c &= \frac{5}{3}
\end{align}
The derivation of these values is developed in appendix \ref{app:ch-rad-Wilkin}

\subsection{Fits to the tail}
\label{sec:fits-tail}

In most cases, the quadric fit to the head of the bowshock does a very poor job of representing the ``wings'' or ``tail''.  The bowshock tail in all cases is asymptotically hyperbolic, with

We therefore 
We carry out three-level nested fits to determine the

For the hyperbola ``center''
\begin{multline}
  \label{eq:tail-analytic-x0}
  x_{0,\mathrm{t}} = 0.7 \beta^{-0.55} \biggl[
    C_3 \bigl(\log_{10}\beta\bigr)^3 + C_2 \bigl(\log_{10}\beta\bigr)^2 
  \\ + C_1 \log_{10}\beta + C_0
  \biggr]
\end{multline}
\begin{equation}
  \label{eq:tail-analytic-x0-minus-a}
  (x_{0,\mathrm{t}} - a_{\mathrm{t}}) = D_2 (\log_{10}\beta)^2 + D_1 \log_{10}\beta + D_0
\end{equation}
where
\begin{alignat}{2}
  \label{eq:tail-analytic-coeffs-c}
  C_k &= c_{2,k} \xi^2 + c_{1,k} \xi + c_{0,k} &\quad \text{for\ } k &= \{0, 1, 2, 3\} \\
  \label{eq:tail-analytic-coeffs-d}
  D_k &= d_{2,k} \xi^2 + d_{1,k} \xi + d_{0,k} &\quad \text{for\ } k &= \{0, 1, 2\}
\end{alignat}

% \newcommand\iso{\ensuremath{^{\mathrm{iso}}}}

% \begin{table}
%   \caption{Coefficients for hyperbola fit to bowshock tails}
%   \label{tab:tail-fit-coeffs}
%   \renewcommand\arraystretch{1.2}
%   \setlength\tabcolsep{0.5\tabcolsep}
%   \begin{tabular}{@{}llll@{}}
%     \toprule
%     Equation~(\ref{eq:tail-analytic-x0}) & 
%     \multicolumn{3}{l}{
%     Equation~(\ref{eq:tail-analytic-coeffs-c}) \dotfill
%     } \\ \midrule
%     \( C\iso_0 = +1.3195     \)    
%     & \( c_{0,0} = +2.0758   \)  
%     & \( c_{1,0} = -0.2309   \)  
%     & \( c_{2,0} = -0.2532   \)\\
%       \( C\iso_1 = +0.4229     \)    
%     & \( c_{0,1} = +0.9571   \)  
%     & \( c_{1,1} = -0.1530   \)  
%     & \( c_{2,1} = -0.2487   \)\\
%       \( C\iso_2 = +0.1092     \)    
%     & \( c_{0,2} = +0.2528   \)  
%     & \( c_{1,2} = -0.0360   \)  
%     & \( c_{2,2} = -0.0794   \)\\
%       \( C\iso_3 = +0.0051     \)    
%     & \( c_{0,3} = +0.0171   \)  
%     & \( c_{1,3} = -0.0010   \)  
%     & \( c_{2,3} = -0.0095   \)\\ \midrule
%     Equation~(\ref{eq:tail-analytic-x0-minus-a}) &
%     \multicolumn{3}{l}{
%     Equation~(\ref{eq:tail-analytic-coeffs-d}) \dotfill
%     } \\ \midrule
%     \( D\iso_0 = +0.7962   \)    
%     & \( d_{0,0} = +0.8516 \)  
%     & \( d_{1,0} = -0.0907 \)  
%     & \( d_{2,0} = -0.2002 \)\\
%       \( D\iso_1 = -0.2363   \)    
%     & \( d_{0,1} = -0.7620 \)  
%     & \( d_{1,1} = +0.1411 \)  
%     & \( d_{2,1} = -0.0295 \)\\
%       \( D\iso_2 = -0.0126   \)    
%     & \( d_{0,2} = -0.0683 \)  
%     & \( d_{1,2} = +0.0390 \)  
%     & \( d_{2,2} = -0.0236 \)\\
%     \bottomrule
%   \end{tabular}
% \end{table}

% \begin{figure*}
%   \centering
%   \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-analytic}
%   \caption{Double quadric fits to thin shell
%     solutions.}
%   \label{fig:head-tail}
% \end{figure*}

% \begin{figure}
%   \centering
%   \includegraphics[width=\linewidth]{figs/two-quadric-th90-vs-i}
%   \caption{Variation with inclination of the body-frame polar angle
%     \(\theta_{90}\) that corresponds to the projected perpendicular radius
%     \(R’_{90}\).  Line colors and thicknesses represent different
%     quadrics of revolution, as in
%     Fig.~\ref{fig:projected-R90-Rc-snapshots}.  This quantity is
%     important because the quadric fits to the bow shock shape must be
%     accurate for \(\theta < \theta_{90}\) in order to give a reliable estimate
%     for \(R’_{90}\).}
%   \label{fig:projected-th90}
% \end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-residuals}
  \caption[]{Residuals of double quadric fits to thin shell solutions.
    Residuals are expressed as the fractional error in the
    complementary angle \(\theta_1\) (see Fig.~\ref{fig:crw-schema}) for
    the same parameters as are shown in Fig.~\ref{fig:head-tail}.}
  \label{fig:head-tail-residuals}
\end{figure*}

\subsection{Projection effects in the thin shell model}
\label{sec:proj-effects-thin}

>>>>

\section{Thin-shell bow shock models}
\label{sec:crw-scenario}

@@

For the wind--wind case, a family of solutions are found that depend on
the value of \(\beta\), the wind momentum ratio,\footnote{%
  By always placing the weaker of the two winds at the origin, it is
  only necessary to consider \(\beta \le 1\).  } %
see Figure~\ref{fig:crw-schema},
equations~(\ref{eq:stagnation-radius}, \ref{eq:beta-definition}), and
surrounding discussion in \S~\ref{sec:intro}.  We propose that these
shapes be called \textit{cantoids}.  The exact solution for the
cantoid shapes (eqs.~[23, 24] of \CRW{}) is only obtainable in
implicit form, but an approximate explicit solution (eq.~[26] of
\CRW{}) is very accurate for \(\beta \le 0.1\).  The wilkinoid shape
corresponds to the \(\beta \to 0\) limit of the cantoids.  Note that \CRW{}
employ cylindrical polar coordinates, \(z\) and \(r\), see our
Figure~\ref{fig:crw-schema}, and we follow this usage for the
thin-shell models discussed in this section.  \CRW{}'s \(z\) axis
corresponds to the cartesian \(x\) axis used in
sections~\ref{sec:projection} and \ref{sec:conic} of the current
paper, while the \(r\) axis corresponds to \(y\) when \(\phi = 0\).

A generalization of the cantoids to the case of an
anisotropic\footnote{Note that the wind anisotropy axis must be
  aligned with the star--star axis to maintain cylindrical symmetry.}
inner wind is developed next, giving rise
to what we call \textit{ancantoids}, which depend on an anisotropy
index, \(k\), in addition to \(\beta\).

\subsection{Bow shocks from anisotropic wind--wind interactions}
\label{sec:ancantoid}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/anisotropic-arrows}
  \caption[]{Schematic diagram of wind flow patterns in isotropic and
    non-isotropic cases for different values of the anisotropy index,
    \(k\).  Arrow length represents the wind momentum loss rate per
    solid angle.}
  \label{fig:anisotropic-arrows}
\end{figure}

We wish to generalize the results of \citet[\CRW{}]{Canto:1996} to the
case where the inner wind is no longer isotropic, but instead has a
density that falls off with angle, \(\theta\), away from the symmetry axis.
Specifically, at some fiducial spherical radius, \(R_0\), from the
origin, the wind mass density is given by
\begin{equation}
  \label{eq:ancantoid-density}
  \rho(R_0, \theta) =
  \begin{cases}
    \rho_0 \cos^k \theta & \text{for \(\theta \le 90^\circ\)} \\
    0 & \text{for \(\theta > 90^\circ\)}
  \end{cases}
  \ ,
\end{equation}
where \(\rho_0\) is the density on the symmetry axis and \(k \ge 0\) is an
\textit{anisotropy index}.  The wind velocity is still assumed to be
constant and the wind streamlines to be radial, so the radial
variation of density at each angle is
\(\rho(R, \theta) = \rho(R_0, \theta)\, (R/R_0)^{-2}\) and the wind mass loss rate and
momentum loss rate per solid angle both have the same \(\cos^k\theta\)
dependence as the density.  Examples are shown in
Figure~\ref{fig:anisotropic-arrows} for a variety of different values
of \(k\).  As \(k\) increases, the wind becomes increasingly jet-like.

Our primary motivation for considering such an anisotropic wind is the
case of the Orion Nebula proplyds and their interaction with the
stellar wind of the massive star \thC{}
\citep{Garcia-Arredondo:2001a}.  The inner ``wind'' in this case is
the transonic photoevaporation flow away from a roughly hemispherical
ionization front, where photoionization equilibrium, together with
monodirectional illumination of the front, implies that the ionized
hydrogen density, \(n\), satisfies \(n^2 \propto \cos \theta\), which is
equivalent to \(k = 0.5\) in equation~\eqref{eq:ancantoid-density}.
Since the primary source of ionizing photons is the same star that is
the source of the outer wind, it is natural that the inner wind's axis
should be aligned with the star--star axis in this case.  For other
potential causes of wind anisotropy (for instance, bipolar flow from
an accretion disk), there is no particular reason for the axes to be
aligned, so cylindrical symmetry would be broken.  Nevertheless, we
calculate results for general \(k\) with aligned axes, so as to
provide a richer variety of cylindrically symmetric bow shock shapes
than are seen in the cantoids.

The general solution for the bow shock shape, \(R(\theta)\), in the \CRW{}
formalism is
\begin{equation}
  R(\theta) = \frac {\dot{J}_{\w} + \dot{J}_{\w{}1}}
  {\left(\dot{\Pi}_{\w{}r}+\dot{\Pi}_{\w{}r1}\right)\cos\theta
    - \left(\dot{\Pi}_{\w{}z}+\dot{\Pi}_{\w{}z1}\right)\sin\theta}
  \label{eq:Rmom}
\end{equation}
where \(\dot{\Pi}_{\w{}r}\), \(\dot{\Pi}_{\w{}z}\), \(\dot{J}_{\w}\) are
the accumulated linear radial momentum, linear axial momentum, and
angular momentum, respectively, due to the inner wind emitted between
the axis and \(\theta\). The equivalent quantities for the outer wind have
subscripts appended with ``1''.  The inner wind momenta for our
anisotropic case (replacing \CRW{}'s eqs.~[9, 10]) are:
\begin{gather}
  \label{eq:ancantoid-momenta}
  \begin{aligned}
    \dot{\Pi}_{\w{}z} &= \frac{k + 1}{2(k+2)}\, \dot{M}_{\w}^0 V_{\w}
    \max\left[\bigl(1- \cos^{k+2} \theta\bigr), 1 \right] \\
    \dot{\Pi}_{\w{}r} &= (k + 1)\, \dot{M}^0_{\w} V_{\w}\, I_k (\theta) 
  \end{aligned}
\end{gather}
where
\begin{equation}
  \label{eq:ancantoid-mass-loss}
  \dot{M}^0_{\w} = \frac{2 \pi} {k + 1} r_0^2 \rho_0 V_{\w}
\end{equation}
is the total mass-loss rate of the inner wind. The integral
\begin{equation}
  \label{eq:ancantoid-I-integral}
  I_k(\theta) = \int^{\max(\theta, \pi/2)}_0 \cos^k \theta \sin^2\theta \,d\theta 
\end{equation}
has an analytic solution in terms of the hypergeometric function,
\({}_2 F_1(-\tfrac12; \tfrac{1+k}2; \tfrac{3+k}2; \cos^2 \theta)\), but is
more straightforwardly calculated by numerical quadrature.  The
angular momentum of the inner wind about the origin is
\(\dot{J}_{\w} = 0\) because it is purely radial.  The outer wind
momenta are unchanged from the \CRW{} case, but are given here for
completeness:
\begin{gather}
  \label{eq:ancantoid-momenta-outer}
  \begin{aligned}
    \dot{\Pi}_{\w{}z1} & =
    -\frac{\dot{M}^0_{\w{}1}V_{\w{}1}}{4}\sin^2\theta_1\\
    \dot{\Pi}_{\w{}r1} & =
    \frac{\dot{M}^0_{\w{}1}V_{\w{}1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)\\
    \dot{J}_{\w{}1} & =
    \frac{\dot{M}^0_{\w{}1}V_{\w{}1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)D \ .
  \end{aligned} 
\end{gather}

We define \(\beta\) in this case as the momentum ratio \emph{on the symmetry axis}, which means that 
\begin{equation}
  \label{eq:ancantoid-momentum-ratio}
  \dot{M}^0_{\w{}1}V_{\w{}1} = 2 (k + 1)\, \beta\, \dot{M}^0_{\w} V_{\w} \ . 
\end{equation}
Substituting
equations~(\ref{eq:ancantoid-momenta}--\ref{eq:ancantoid-momentum-ratio})
into equation~\eqref{eq:Rmom} and making use of the geometric relation
between the interior angles of the triangle shown in
Figure~\ref{fig:crw-schema}:
\begin{equation}
  \label{eq:crw-angles}
  R \sin(\theta + \theta_1) = D \sin \theta_1 \ , 
\end{equation}
yields
\begin{equation}
  \label{eq:ancantoid-theta-theta1-implicit}
  \theta_1 \cot \theta_1 = 1 +
  2 \beta \left(
    I_k(\theta) \cot \theta
    - \frac{1 - \cos^{k+2} \theta} {k + 2} \right)   \ , 
\end{equation}
which is the generalization of \CRW{}'s equation~(24) to the
anisotropic case.  Equation~\eqref{eq:ancantoid-theta-theta1-implicit}
is solved numerically to give \(\theta_1(\theta)\), which is then combined with
equations~(\ref{eq:crw-angles}) and (\ref{eq:stagnation-radius}) to
give the dimensionless bow shape, \(R(\theta; \beta, k)/R_0\), where we now
explicitly indicate the dependence of the solution on two parameters:
axial momentum ratio, \(\beta\), and anisotropy index, \(k\).  We refer to
the resultant bow shapes as \textit{ancantoids}.

%The most notable scenarios, since they have astrophysical relevance are the following:
%$k=1/2$ ak.a. the ``proplyd case'', following \citep{HA:1998}, and $k=0$, ak.a, the ``isotropic case'', following \CRW{}. The comparison between both solutions
%is shown in figure (\ref{fig:r-beta}), along with an extreme anisotropy case.

@@

\subsection{True shapes of cantoids and ancantoids}
\label{sec:true-cantoids-ancantoids}

The resulting shapes are shown in
Figure~\ref{fig:r-beta} for three different values of \(\beta\).  There is
a general tendency for the bows to be flatter and more open with
increasing \(\beta\), while at a given \(\beta\) it is the cantoid (black
lines) that is most open

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/ancantoid-angles}
  \caption{Equivalent quadric angles, \(\theta_{\Q}\), for ancantoids and
    cantoids.  Solid lines show values of \(\theta_{\Q}\) calculated from
    \((\Pi, \Lambda)\), which is representative of the shape of the head,
    while dashed lines show \(\theta_{\Q}\) calculated from
    \(\theta_\infty\), which is representative of the tail.  Dot-dashed line
    shows the result for cantoids, which differ from the \(k=0\)
    ancantoids in \(\theta_\infty\), but not in \((\Pi, \Lambda)\). Gray shading and
    line colors have the same meaning as in
    Fig.~\ref{fig:ancantoid-Pi-lambda-true}. }
  \label{fig:ancantoid-angles}
\end{figure}

% \subsection{Characteristic Radii}
% $R_0$ is obtained directly from equation (27) of \CRW{} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.
% %Here goes a little introduction
% For the rest of the radii we need a relation between $\theta$ and $\theta_1$ as follows:

% \begin{align}
% \theta_1\cot\theta_1 -1 = 2\beta I_k(\theta) \cot\theta - \frac{2\beta}{k+2}\left(1-\cos^{k+2}\theta\right)
% \label{eq:th1th}
% \end{align}

% Equation (\ref{eq:th1th}) is reduced to equation (24) of \CRW{} when $k=0$.
% We can obtain $R_{90}$ by following the process shown in appendix \ref{app:r90-analytic},
% which lead us to a solution for $B \equiv \frac{R_{90}}{R_0}$:

% \begin{align}
% \tilde{R}_{90} = \frac{\sqrt(3\xi)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
% \label{eq:B}
% \end{align}

% Now, the solution for $R_c$ is explained in appendix \ref{app:rc-analytic},
% which lead us to derive the radius of curvature at the symmetry axis:

% \begin{align}
% R_c &= R_0\left(1-2\gamma\right)^{-1} \label{eq:Rcurv} \\
% \mathrm{where:~} & \gamma = \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}(1-2\beta^{1/2})
% \end{align}

% Finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of
% conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (\ref{eq:Thc})

% \begin{align}
% \tan^2\theta_c &= \left| \frac{3\xi\left(1+\beta^{1/2}\right)^2}{\left(1-\xi\beta\right)^2\left(1+\frac{1}{5}\xi\beta\right)}-\frac{2}{\left(1-2\gamma\right)}\right| 
% \label{eq:thc-CRW}
% \end{align}

% \begin{figure}
% \begin{tabular}{c}
% \includegraphics[width=\linewidth]{figs/AB-beta-log} \\
% \includegraphics[width=\linewidth]{figs/thc-beta-log}
% \end{tabular}
% \caption{Top: Characteristic radii, $\tilde{R}_c = R_c/R_0$ (solid lines) and $\tilde{R}_{90}
%   = R_{90}/R_0$ (dashed lines)
%   vs $\beta$, calculated from quadric fits to the generalized CRW
%   solutions with varying degrees of isotropy $\xi$.  Bottom: Conic
%   angle $\theta_c$ vs $\beta$ for the bow 
%   shock head (solid lines) and the bow shock tail (dashed lines).}
% \label{fig:rad-beta}
% \end{figure}

% % Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii,
% %being $R_0$ the
% %easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).

% With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
% momenta and different density distributions. Figure \ref{fig:rad-beta} shows equations ( \ref{eq:B}), (\ref{eq:Rcurv}) and (\ref{eq:thc-CRW}) for different anisotropy indexes.

% \subsection{Special Case: Isotropic Wind/Parallel Flow Interaction Problem}

% This problem has already been solved in \citet{Wilkin:1996a} and \CRW{}, which have an explicit form for the shell shape, given by:

% \begin{align}
%   R(\theta) = R_0\csc\theta\left[3(1-\theta\cot\theta)\right]^{1/2} \label{eq:R-Wilkin}
% \end{align}
% Where:
% \begin{align}
%   R_0 = \left(\frac{\dot{M}_wv_w}{4\pi\rho_a v_a^2}\right)^{1/2}
% \end{align}
% And $\rho_a$ and $v_a$ being the density and the velocity of the Parallel wind, respectively.
% The characteristic radii are given by:
% \begin{align}
%   \tilde{R}_{90} &= \sqrt{3} \\
%   \tilde{R}_c &= \frac{5}{3}
% \end{align}
% The derivation of these values is developed in appendix \ref{app:ch-rad-Wilkin}

% \subsection{Fits to the tail}
% \label{sec:fits-tail}

% In most cases, the quadric fit to the head of the bowshock does a very poor job of representing the ``wings'' or ``tail''.  The bowshock tail in all cases is asymptotically hyperbolic, with

% We therefore 
% We carry out three-level nested fits to determine the

% For the hyperbola ``center''
% \begin{multline}
%   \label{eq:tail-analytic-x0}
%   x_{0,\mathrm{t}} = 0.7 \beta^{-0.55} \biggl[
%     C_3 \bigl(\log_{10}\beta\bigr)^3 + C_2 \bigl(\log_{10}\beta\bigr)^2 
%   \\ + C_1 \log_{10}\beta + C_0
%   \biggr]
% \end{multline}
% \begin{equation}
%   \label{eq:tail-analytic-x0-minus-a}
%   (x_{0,\mathrm{t}} - a_{\mathrm{t}}) = D_2 (\log_{10}\beta)^2 + D_1 \log_{10}\beta + D_0
% \end{equation}
% where
% \begin{alignat}{2}
%   \label{eq:tail-analytic-coeffs-c}
%   C_k &= c_{2,k} \xi^2 + c_{1,k} \xi + c_{0,k} &\quad \text{for\ } k &= \{0, 1, 2, 3\} \\
%   \label{eq:tail-analytic-coeffs-d}
%   D_k &= d_{2,k} \xi^2 + d_{1,k} \xi + d_{0,k} &\quad \text{for\ } k &= \{0, 1, 2\}
% \end{alignat}

% % \newcommand\iso{\ensuremath{^{\mathrm{iso}}}}

% % \begin{table}
% %   \caption{Coefficients for hyperbola fit to bowshock tails}
% %   \label{tab:tail-fit-coeffs}
% %   \renewcommand\arraystretch{1.2}
% %   \setlength\tabcolsep{0.5\tabcolsep}
% %   \begin{tabular}{@{}llll@{}}
% %     \toprule
% %     Equation~(\ref{eq:tail-analytic-x0}) & 
% %     \multicolumn{3}{l}{
% %     Equation~(\ref{eq:tail-analytic-coeffs-c}) \dotfill
% %     } \\ \midrule
% %     \( C\iso_0 = +1.3195     \)    
% %     & \( c_{0,0} = +2.0758   \)  
% %     & \( c_{1,0} = -0.2309   \)  
% %     & \( c_{2,0} = -0.2532   \)\\
% %       \( C\iso_1 = +0.4229     \)    
% %     & \( c_{0,1} = +0.9571   \)  
% %     & \( c_{1,1} = -0.1530   \)  
% %     & \( c_{2,1} = -0.2487   \)\\
% %       \( C\iso_2 = +0.1092     \)    
% %     & \( c_{0,2} = +0.2528   \)  
% %     & \( c_{1,2} = -0.0360   \)  
% %     & \( c_{2,2} = -0.0794   \)\\
% %       \( C\iso_3 = +0.0051     \)    
% %     & \( c_{0,3} = +0.0171   \)  
% %     & \( c_{1,3} = -0.0010   \)  
% %     & \( c_{2,3} = -0.0095   \)\\ \midrule
% %     Equation~(\ref{eq:tail-analytic-x0-minus-a}) &
% %     \multicolumn{3}{l}{
% %     Equation~(\ref{eq:tail-analytic-coeffs-d}) \dotfill
% %     } \\ \midrule
% %     \( D\iso_0 = +0.7962   \)    
% %     & \( d_{0,0} = +0.8516 \)  
% %     & \( d_{1,0} = -0.0907 \)  
% %     & \( d_{2,0} = -0.2002 \)\\
% %       \( D\iso_1 = -0.2363   \)    
% %     & \( d_{0,1} = -0.7620 \)  
% %     & \( d_{1,1} = +0.1411 \)  
% %     & \( d_{2,1} = -0.0295 \)\\
% %       \( D\iso_2 = -0.0126   \)    
% %     & \( d_{0,2} = -0.0683 \)  
% %     & \( d_{1,2} = +0.0390 \)  
% %     & \( d_{2,2} = -0.0236 \)\\
% %     \bottomrule
% %   \end{tabular}
% % \end{table}

% % \begin{figure*}
% %   \centering
% %   \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-analytic}
% %   \caption{Double quadric fits to thin shell
% %     solutions.}
% %   \label{fig:head-tail}
% % \end{figure*}

% % \begin{figure}
% %   \centering
% %   \includegraphics[width=\linewidth]{figs/two-quadric-th90-vs-i}
% %   \caption{Variation with inclination of the body-frame polar angle
% %     \(\theta_{90}\) that corresponds to the projected perpendicular radius
% %     \(R’_{90}\).  Line colors and thicknesses represent different
% %     quadrics of revolution, as in
% %     Fig.~\ref{fig:projected-R90-Rc-snapshots}.  This quantity is
% %     important because the quadric fits to the bow shock shape must be
% %     accurate for \(\theta < \theta_{90}\) in order to give a reliable estimate
% %     for \(R’_{90}\).}
% %   \label{fig:projected-th90}
% % \end{figure}

% \begin{figure*}
%   \centering
%   \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-residuals}
%   \caption[]{Residuals of double quadric fits to thin shell solutions.
%     Residuals are expressed as the fractional error in the
%     complementary angle \(\theta_1\) (see Fig.~\ref{fig:crw-schema}) for
%     the same parameters as are shown in Fig.~\ref{fig:head-tail}.}
%   \label{fig:head-tail-residuals}
% \end{figure*}

% \subsection{Projection effects in the thin shell model}
% \label{sec:proj-effects-thin}
